\LARGE \bf Approximately Orchestrated Routing and Transportation Analyzer:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
misc tweaks

Every step, a generator creates some number of new agents. The generator either
immediately performs any timely computation required by the agent's route
policy, such as pathfinding, or delegates it to a pool of worker threads to
process in the background.  Once an agent's route is ready, the agent waits
alongside its starting lane (as if it is in a driveway or parking lot). When the
lane has no agents that could potentially crash with the new vehicle, the new
agent enters the system.
%with zero initial speed. Because behaviors must enforce speed limit along a lane
%from the moment an agent enters a road, it is safe for a new agent to enter a
%road if there is no other agent within the worst-case distance (traveling
%distance at the speed limit, plus stopping distance from this speed) preceeding
%the spawn point. To avoid predicting which agents might enter the lane in the
%near future, there is a buffer space at the beginning of the lane where a new
%agent may never spawn. This disqualifies some short lanes from being spawn
%points, but this is not a big limitation in practice. \commentpk{I understand
%your concern about explaining the entire methodology, but the last 2 lines are
%unnecessary and somewhat distracting}

@@

A behavior interacts with an intersection policy by sending it the agent's
desired turn, the agent's speed, the current distance from the start of the
intersection, and the length of time the agent has been idling at zero speed.
The policy replies by ordering the agent to ``stop'' or ``proceed''. The
behavior will continue to statelessly poll the policy every step until the agent
begins the turn. The policy may approve an agent for entry one step and deny it
the next, so long as the agent could safely brake without danger of entering the
intersection. The policy is free to allow concurrent turns in any arrangement
by different agents as long as no two simultaneous turns conflict.

@@

In many observed cases, the gridlock is caused by AORTA's present lack of
lane-changing support: agents loop around these intersections in order to enter
a lane adjacent to their original lane. Since these routes are still legal, it
is desirable to prevent or mend this without forcing different routes. However,
choosing alternative moves (by changing lanes or rerouting) is one sufficient,
but not necessarily required, condition for liveness \cite{AAAI11-au}.
\commentd{I misinterpreted the results of the paper originally. Is this a safer
and more relevant claim to make?}

@@

A particular focus of AORTA is intersection policies. To demonstrate how much
policy affects the throughput of intersections and total performance of the
transportation system, three policies are evaluated: stop sign, traffic signal,
and autonomous reservation. Every intersection uses the same policy.

@@

The experiment simulates a 6 by 7 mile slice of downtown Austin,
Texas\footnote{bounded by the Mopac and Springdale Road horizontally, and Oltorf
Street and Koenig Lane vertically}, for one hour. The step duration is fixed at
0.1 seconds. While the intersection policies vary, the agents spawned and their
routes remain the same. A generator creates one new agent every 1 simulation
second, with a uniformly random starting position and goal.
\commentd{Chiu asked about the distribution of incoming agents. Is ``uniformly
random start and end'' not clear?}

@@

Stop signs accept agents first-come, first-served, refusing agents until they
have idled at 0 speed for 1 second. This delay approximates human reaction time.

The traffic signal policy requires timings and groups of simultaneous turns for
each intersection. The heuristic evaluated uses standard turn groups (turns from
parallel incoming directions are scheduled simultaneously, and left turns are
grouped) and employs breadth-first search to propagate timings. The goal is to
synchronize green signals so agents in some lanes do not stop for several
intersections.
\commentd{chiu recommends more details with how we propagate timings. Thoughts,
Mike?}
\commentc{You can mention about using optimized traffic signal timings generated
  by commercial traffic signal optimization packages such as SYNCHRO (cite
  Husch, D. and Albeck, J. (2004) Trafficware Synchro 6 User Guide, TrafficWare,
  Albany, California.)
}

\commentd{advice on wording?}
Finally, in anticipation of the advent of autonomous vehicles, an autonomous
reservation policy inspired by AIM \cite{JAIR08-dresner} is tested. This policy
groups agents with compatible turns together, allowing new agents to join
existing groups. To prevent one heavy direction of traffic from hogging the
intersection indefinitely, a timeout preemptively cycles through reservations.

@@

If an intersection immediately permits an agent to proceed and grants other
agents in the same lane similar access (because this new agent must still follow
these others), then the new agent may simply proceed at full speed limit without
pausing. This gives the least possible delay spent along some lane, so any extra
time is defined as lag and is used to measure intersection performance. Figure
\ref{fig:avg_lag} graphs the average of this delay per agent. On average,
reservation policies cause less than 1 second of delay at each intersection,
stop signs cause about 7 seconds lag, and traffic signals cause 16 seconds.
\commentd{We need to be clear that our traffic lights suck, so this number is
pretty biased.}

>>>>

Every step, a generator creates some number of new agents. The generator either
immediately performs any timely computation required by the agent's route
policy, such as pathfinding, or delegates it to a pool of worker threads to
process in the background.  Once an agent's route is ready, the agent waits
alongside its starting lane (as if it is in a driveway or parking lot). When the
lane has no agents that could potentially crash with the new vehicle, the new
agent enters the system.

@@

A behavior interacts with an intersection policy by sending it the agent's
desired turn, the agent's speed, the current distance from the start of the
intersection, and the length of time the agent has been idling at rest. The
policy replies by ordering the agent to ``stop'' or ``proceed''. The behavior
will continue to statelessly poll the policy every step until the agent begins
the turn. The policy may approve an agent for entry one step and deny it the
next, so long as the agent could safely brake without danger of entering the
intersection. The policy is free to allow concurrent turns in any arrangement by
different agents as long as no two simultaneous turns conflict.

@@

In many observed cases, the gridlock is caused by AORTA's present lack of
lane-changing support: agents loop around these intersections in order to enter
a lane adjacent to their original lane. Since these routes are still legal, it
is desirable to prevent or mend this without forcing different routes.
However, choosing alternative moves (by changing lanes or rerouting) is an
important constituent of a sufficient condition for the liveness of a road
network cite{AAAI11-au}.

@@

A particular focus of AORTA is intersection policies. To demonstrate how
policy affects the throughput of intersections and total performance of the
transportation system, three policies are evaluated: stop sign, traffic signal,
and autonomous reservation. Every intersection uses the same policy.

@@

The experiment simulates a 9$\times$11km$^{2}$ slice of downtown Austin,
Texas\footnote{bounded by the Mopac and Springdale Road horizontally, and Oltorf
Street and Koenig Lane vertically}, for one hour. The step duration is fixed at
0.1 seconds. While the intersection policies vary, the agents spawned and their
routes remain the same. A generator creates one new agent every 1 simulation
second, with a uniformly random starting position and goal.

@@

Stop signs accept agents first-come, first-served, refusing agents until they
have idled at rest for 1 second. This delay approximates human reaction time.

The traffic signal policy requires timings and groups of simultaneous turns for
each intersection. The heuristic currently assigning these arbitrarily picks one
major road, schedules turns from that road to others, then repeats the process
from all reachable roads using a breadth-first search. By estimating how long
performing one turn and traveling along the next lane takes, the timing of the
next intersection can be scheduled so that agents from the first road continue
traveling without stopping for several consecutive intersections. This heuristic
is far from optimal, meaning the performance of traffic signals described below
could be improved, perhaps by incorporating packages such as SYNCHRO
\cite{synchro}.

The last policy tested is an autonomous reservation policy inspired by AIM
\cite{JAIR08-dresner}. This policy groups agents with compatible turns together,
allowing new agents to join existing groups. To prevent one heavy direction of
traffic from hogging the intersection indefinitely, a timeout preemptively
cycles through reservations.

@@

If an intersection immediately permits an agent to proceed and grants other
agents in the same lane similar access (because this new agent must still follow
these others), then the new agent may simply proceed at full speed limit without
pausing. This gives the least possible delay spent along some lane, so any extra
time is defined as lag and is used to measure intersection performance. Figure
\ref{fig:avg_lag} graphs the average of this delay per agent. On average,
reservation policies cause less than 1 second of delay at each intersection,
stop signs cause about 7 seconds lag, and traffic signals using the heuristic
described above cause 16 seconds. These results will vary with different
traffic levels and policy configurations, so the important demonstration is that
AORTA can be used as a framework for evaluating these policies.
